checkData

### 2023-08-23 analysis/checkData.Rmd
applies sampleID change to tibble

```{r setup, include=FALSE}
library(tidyverse)
library(here)
```

@@

#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
d_journals %>% 
  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
  mutate(sampleID = case_when(
    sample_journal_both == "both" ~ "both",
    sample_journal_both == "na" ~ sample_journal_prominent,
    TRUE ~ sample_journal_both
  )) %>%
  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(tidylog)
```

@@

#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
d_journals <- d_journals %>% 
  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
  mutate(sampleID = case_when(
    sample_journal_both == "both" ~ "both",
    sample_journal_both == "na" ~ sample_journal_prominent,
    TRUE ~ sample_journal_both
  )) %>%
  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))
